Quantum Pseudo-Telepathy

### 2023-06-07 paper/main.tex
Simplifying quantum example

      +1, \text{ proj. onto } \{\ket{i0jk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2} \\
      -1, \text{ proj. onto } \{\ket{i1jk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2},

@@

  Suppose that Alice has observed \(+1\). Notice that
  only two of the components of the \(+1\)-eigenspace are seen in the
  initial state \(\ket{\psi}\): \(\ket{0000}\) and
  \(\ket{1010}\). Therefore, \(\ket{\psi}\) collapses to

@@

      +1, \text{ proj. onto } \{\ket{0ijk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2} \\
      -1, \text{ proj. onto } \{\ket{1ijk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } \frac{1}{2}.

@@

  Suppose, now, that Alice has observed the outcome \(-1\). Notice that
  only one component of the \(-1\)-eigenspace is seen in the state
  \(\ket{\psi}_{A1}\). Hence, the state collapses to

@@

  only possible outcomes is

@@

      -1, \text{ proj. onto } \{\ket{i\overline{i}jk} \mid i, j, k \in \{0, 1\}\}
        \text{ with prob. } 1,

@@

  where \(\overline{i}\) is the \texttt{not} operator. Notice that,
  because \(\ket{\psi}_{A2}\) falls exactly into the
  \(-1\)-eigenspace, the only possible outcome is \(-1\), and the
  state does not change, i.e. \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).
  Alice, then, fills the first row with the values \(\{+1, -1, -1\}\),
  whose product is, as required, \(+1\). Upon receiving Alice's
  answer, Charlie goes to meet Bob. Suppose he assigns the second
  column to Bob. To fill in the value of the first cell (which is the
  intersection of the first row and second column), Bob measures the
  observable \(Z \otimes I\). Notice that \(\ket{\psi}_{A3}\) is
  entirely in the \(-1\)-eigenspace; thus, Bob will for sure observe
  the outcome \(-1\) ---~which matches Alice's answer~--- and the
  state will not change: \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving
  on to the second cell, Bob measures the observable \(I \otimes X\),
  whose possible outcomes are (for readability, we are showing only
  the components of the eigenspaces that are not orthogonal to
  \(\ket{\psi}_{B1}\))

@@

      +1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011})
        \text{ with prob. } \frac{1}{2} \\
      -1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} - \ket{1011})
        \text{ with prob. } \frac{1}{2}.

@@

  The only possible outcome is

@@

      +1, \text{ proj. onto } \frac{1}{\sqrt{2}}(\ket{1010} + \ket{1011})
      \text{ with prob. } 1,

@@

  and the state does not change, i.e.
  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Alice's answer satisfies the
  property of the rows (that the product of the entries is equal to
  \(+1\)) and Bob's answer satisfies the property of the columns
  (product is equal to \(-1\)).  Moreover, Alice and Bob agreed in the
  intersection of the row and the column.  Hence, they won this round!

>>>>

      +1 \left(I \otimes \ketbra{0}{0} \otimes I \otimes I\right)
        &\text{with probability } \frac{1}{2} \\
      -1 \left(I \otimes \ketbra{1}{1} \otimes I \otimes I\right)
        &\text{with probability } \frac{1}{2},

@@

  Suppose that Alice has observed \(+1\). In this case, the initial
  state \(\ket{\psi}\) collapses to

@@

      +1 \left(\ketbra{0}{0} \otimes I \otimes I \otimes I\right)
        &\text{with probability } \frac{1}{2} \\
      -1 \left(\ketbra{1}{1} \otimes I \otimes I \otimes I\right)
        &\text{with probability } \frac{1}{2}.

@@

  Suppose, now, that Alice has observed the outcome \(-1\). The state

@@

  possible outcomes are

@@

      +1 \left(\left(\ketbra{00}{00} + \ketbra{11}{11}\right) \otimes I \otimes I\right)
      &\text{with probability } 0 \\
      -1 \left(\left(\ketbra{01}{01} + \ketbra{10}{10}\right) \otimes I \otimes I\right)
      &\text{with probability } 1.

@@

  Notice that the only possible outcome that Alice can observe is
  \(-1\), and the state does not change, i.e.
  \(\ket{\psi}_{A3} = \ket{\psi}_{A2}\).  Alice, then, fills the first
  row with the values \(\{+1, -1, -1\}\), whose product is, as
  required, \(+1\). Upon receiving Alice's answer, Charlie goes to
  meet Bob. Suppose he assigns the second column to Bob. To fill in
  the value of the first cell (which is the intersection of the first
  row and second column), Bob measures the observable \(Z \otimes
  I\). The only possible outcome, considering the state
  \(\ket{\psi}_{A3}\), is \(-1\) ---~which matches Alice's answer~---
  and the state will not change again:
  \(\ket{\psi}_{B1} = \ket{\psi}_{A3}\). Moving on to the second cell,
  Bob measures the observable \(I \otimes X\), whose possible outcomes
  are

@@

      +1 \left(I \otimes I \otimes I \otimes \ketbra{+}{+}\right)
      &\text{with probability } \frac{1}{2} \\
      -1 \left(I \otimes I \otimes I \otimes \ketbra{-}{-}\right)
      &\text{with probability } \frac{1}{2}.

@@

  The possible outcomes are

@@

      +1 \left(I \otimes I \otimes \left(\ketbra{1+}{1\!+\!} + \ketbra{0-}{0\!-\!}\right)\right)
      &\text{with prob. } 1 \\
      -1 \left(I \otimes I \otimes \left(\ketbra{1-}{1\!-\!} + \ketbra{0+}{0\!+\!}\right)\right)
      &\text{with prob. } 0.

@@

  Bob will for sure observe the outcome \(+1\) and the state does not
  change, i.e.  \(\ket{\psi}_{B3} = \ket{\psi}_{B2}\). Therefore, Bob
  answers \(\{-1, +1, +1\}\). Alice's answer satisfies the property of
  the rows (that the product of the entries is equal to \(+1\)) and
  Bob's answer satisfies the property of the columns (product is equal
  to \(-1\)).  Moreover, Alice and Bob agreed in the intersection of
  the row and the column.  Hence, they won this round!
